% Manually add Bibliography to the TOC
\clearpage
\addcontentsline{toc}{chapter}{Bibliography}

% Bibliography starts here
\begin{thebibliography}{99}
	\bibitem{bibl_1}
		{Mehdi S. M. Sajjadi, Morteza Alamgir, Ulrike von Luxburg. \emph{Peer Grading in a Course on Algorithms and Data Structures: Machine Learning Algorithms do not Improve over Simple Baselines.} In \emph{Proceedings of the Third (2016) ACM Conference on Learning @ Scale,} pp. 369-378, 2016.}
	\bibitem{bibl_2}
		{Siddharth Reddy, Igor Labutov, Thorsten Joachims. \emph{Learning Representations of Student Knowledge and Educational Content.} \emph{Cornell University,} 2015.}
	\bibitem{bibl_2_1}
		{Michael Wu. \emph{The Synthetic Student: A Machine Learning Model to Simulate MOOC Data,} MASSACHUSETTS INSTITUTE OF TECHNOLOGY, 2015.}
	\bibitem{bibl_3}
		{Saeed Hosseini Teshnizi and Sayyed Mohhamad Taghi Ayatollahi. \emph{A Comparison of Logistic Regression Model and Artificial Neural Networks in Predicting of Student’s Academic Failure.} In \emph{Acta Inform Med., } 23(5): 296–300, 2015 Oct.}
	\bibitem{bibl_4}
		{Jeng-Fung Chen, Ho-Nien Hsieh and Quang Hung Do. \emph{Predicting Student Academic Performance: A Comparison of Two Meta-Heuristic Algorithms Inspired by Cuckoo Birds for Training Neural Networks}. In \emph{Algorithms,} 7(4), 538-553, 2014.}
	\bibitem{bibl_5}
		{B.A., Kalejaye, O., Folorunso and O.L., Usman. \emph{Predicting Students' Grade Scores Using Training Functions of Artificial Neural Network}. In \emph{Journal of Natural Sciences, Engineering and Technology, Volume 14,} 2015.}
	\bibitem{bibl_6}
		{V.O. Oladokun, Ph.D., A.T. Adebanjo, B.Sc., and O.E. Charles-Owaba, Ph.D. \emph{Predicting Students’ Academic Performance using Artificial Neural Network: A Case Study of an Engineering Course}. In \emph{The Pacific Journal of Science and Technology, Volume 9,} pp. 72-79, 2008.}
	\bibitem{bibl_7}
		{Emaan Abdul Majeed and Khurum Nazir Junejo. \emph{GRADE PREDICTION USING SUPERVISED MACHINE LEARNING TECHNIQUES.} In \emph{E-Proceedin of the 4th Global Summit on Education,} pp. 224-234, 2016.}
	\bibitem{bibl_8}
		{Amelia Zafra and Sebastián Ventura. \emph{Predicting Student Grades in Learning Management 
		Systems with Multiple Instance Genetic Programming.} In \emph{Educational Data Mining,} 2009.}
	\bibitem{bibl_9}
		{Bin Xu and Dan Yang. \emph{Motivation Classification and Grade Prediction for MOOCs Learners.} In \emph{Comput Intell Neurosci,} 2016 Jan.}
	\bibitem{hughes}
		{G. Hughes. \emph{On the mean accuracy of statistical pattern recognizers}. \emph{In IEEE Transactions on Information Theory, Volume 14,} pp. 55-63, 1968.}
	\bibitem{n_hidden}
		{K. Gnana Sheela and S. N. Deepa. \emph{Review on Methods to Fix Number of Hidden Neurons in Neural Networks}. In \emph{Mathematical Problems in Engineering Volume 2013, Article ID 425740,} 2013.}
\end{thebibliography}
